Verifying Demonstrations

### 2019-02-19 paper/distance-bounding.tex
Fixes typo in \cref to protocol section

The majority of the existing \ac{DB} protocols are symmetric and thus require an honest verifier.
Indeed, in this context it does not make sense to protect against the verifier as he can easily impersonate the prover as he has a knowledge of his secret key.
There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
Our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will potentially try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to 
their actions, thus we also require strong privacy.
In fact, as the construction in \cref{CROCUS} shows, we require \iac{DB} 
\ac{ZKPK}, or simply \ac{PPK}, for discrete logarithms.

>>>>

The majority of the existing \ac{DB} protocols are symmetric and thus require an honest verifier.
Indeed, in this context it does not make sense to protect against the verifier as he can easily impersonate the prover as he has a knowledge of his secret key.
There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
Our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will potentially try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to 
their actions, thus we also require strong privacy.
In fact, as the construction in \cref{Protocol} shows, we require \iac{DB} 
\ac{ZKPK}, or simply \ac{PPK}, for discrete logarithms.
For this paper, we assume the existence of such a protocol. Candidates for such a protocol include modifications of ~\cite{ProProx} or \cite{PROPS} to work for discrete logarithm and to provide general attribute-based anonymous credentials (not restricted to identity-based ones), respectively.

### 2019-02-19 paper/protocol.tex

Several entities are involved in our protocol.
First, \iac{CA} is responsible for certifying a one-to-one mapping between a 
person's identity and a cryptographic key\footnote{%
  This can be done by any \emph{logically} centralized 
  authority~\cite{SybilAttack}.
  Although a decentralized authority, as in the case of a collective 
  authority~\cite{collective-signing} powered by 
  proof-of-personhood~\cite{proof-of-personhood}, would be desirable, we think 
  that this has scalability issues.
  See the detailed discussion in \cref{identity-limits}.
  We will also return to this topic in \cref{Discussion}.
}.
The \ac{CA} is only involved in the setup phase.

>>>>

Several entities are involved in our protocol.
First, \iac{CA} is responsible for certifying a one-to-one mapping between a 
person's identity and a cryptographic key\footnote{%
  This can be implemented using any \ac{CA} that prevents Sybil 
  attacks~\cite{SybilAttack} and ensures a one-to-one mapping between a person 
  and a cryptographic key.
  \Ie for each identity it issues one-and-only-one cryptographic key.
}.
The \ac{CA} is only involved in the setup phase.
